\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-26 syntax.tex
bugfix

Note that we are actually using predicative universe, so we actually
have different levels of universes $\cU_j$. However, we omit universe levels in our latex presentation for conciseness and accessibility.
% Most of the reasoning can be formulated using the \textit{algebra} of QIIT (mapping out function from this quotient data-type).

@@

$$
\Rule[name=Bool]
{}
{\goodTerm{\Gamma}{"tt", "ff"}{\cB}}
\quad
\Rule[]
{\goodSub{\Gamma}{\gamma}{\Delta}}
{\goodType{\Gamma}{(El \ T)[\gamma] \equiv El \ (T[\gamma]) }{j} \quad
 \goodTerm{\Gamma}{"tt"[\gamma] \equiv "tt"}{\cB} \quad 
 \goodTerm{\Gamma}{"ff"[\gamma] \equiv "ff"}{\cB} 
}
$$
\judgebox{\goodSub{\Gamma}{\sigma}{\Delta}}
$$
\Rule[name=Ept Subst]
{}{\goodSub{\Gamma}{\epsilon}{\cdot}}
\quad
\Rule[]
{}{\goodSub{\Gamma}{"id"}{\Gamma}}
\quad
\Rule[name=Sub Comp]{
  \goodSub{\Delta}{\delta}{\Theta}
  \quad \goodSub{\Gamma}{\gamma}{\Delta} 
}{\goodSub{\Gamma}{\delta \circ \gamma}{\Theta}}
\Rule[name=Sub Extend]
{\goodSub{\Gamma}{\gamma}{\Delta} \quad \goodTerm{\Gamma}{t}{A[\sigma]}}
{\goodSub{\Gamma}{(\gamma, t)}{(\Delta, A)}}
$$

@@

A term $\goodTerm{\Gamma}{t}{A}$ can be understood as one term $t$ of
type $A$, with a bunch of holes (of type $\Gamma$) inside the term $t$.
A \textbf{simultaneous substitution} $\goodSub{\Gamma}{\gamma}{\Delta}$ can be similarly
understood in the way that $\gamma$ will output a \textbf{series} of
(dependently-typed related) terms of types $\Delta$, parametrized by
$\Gamma$ (i.e., we can consider there are holes of type $\Gamma$ in $\gamma$).
Thus (1) \ruleref{Sub Extend} looks like concatenating one
series of terms with a new term (the weird looking type of
$\goodTerm{\Gamma}{t}{A[\sigma]}$ in the premise is due to our need of type $A$ in
the context $\Delta$ so that we can use \ruleref{Context Extension} to
create new context); (2) we have \ruleref{Proj Subst-1} to extract a
subpart of a given substitution; (3) \ruleref{Proj-Ext} explains why
substitution really looks like a (deeply-nested) pair.

>>>>

Note that we are actually using predicative universe, so we actually
have different levels of universes $\cU_j$. However, we omit universe levels in our latex presentation for conciseness and readability.
% Most of the reasoning can be formulated using the \textit{algebra} of QIIT (mapping out function from this quotient data-type).

@@

$$
\Rule[name=Bool]
{}
{\goodTerm{\Gamma}{"tt", "ff"}{\cB}}
\quad
\Rule[]
{\goodSub{\Gamma}{\gamma}{\Delta}}
{\goodType{\Gamma}{(El \ T)[\gamma] \equiv El \ (T[\gamma]) }{j} \quad
 \goodTerm{\Gamma}{"tt"[\gamma] \equiv "tt"}{\cB} \quad 
 \goodTerm{\Gamma}{"ff"[\gamma] \equiv "ff"}{\cB} 
}
$$
\judgebox{\goodSub{\Gamma}{\sigma}{\Delta}}
$$
\Rule[name=Ept Subst]
{}{\goodSub{\Gamma}{\epsilon}{\cdot}}
\quad
\Rule[]
{}{\goodSub{\Gamma}{"id"}{\Gamma}}
\quad
\Rule[name=Sub Comp]{
  \goodSub{\Delta}{\delta}{\Theta}
  \quad \goodSub{\Gamma}{\gamma}{\Delta} 
}{\goodSub{\Gamma}{\delta \circ \gamma}{\Theta}}
\Rule[name=Sub Extend]
{\goodSub{\Gamma}{\gamma}{\Delta} \quad \goodTerm{\Gamma}{t}{A[\gamma]}}
{\goodSub{\Gamma}{(\gamma, t)}{(\Delta, A)}}
$$

@@

A term $\goodTerm{\Gamma}{t}{A}$ can be understood as one term $t$ of
type $A$, with a bunch of holes (of type $\Gamma$) inside the term $t$.
A \textbf{simultaneous substitution} $\goodSub{\Gamma}{\gamma}{\Delta}$ can be similarly
understood in the way that $\gamma$ will output a \textbf{series} of
(dependently-typed related) terms of types $\Delta$, parametrized by
$\Gamma$ (i.e., we can consider there are holes of type $\Gamma$ in $\gamma$).
Thus (1) \ruleref{Sub Extend} looks like concatenating one
series of terms with a new term (the weird-looking type of
$\goodTerm{\Gamma}{t}{A[\gamma]}$ in the premise is due to our need of type $A$ in
the context $\Delta$ so that we can use \ruleref{Context Extension} to
create new context); (2) we have \ruleref{Proj Subst-1} to extract a
subpart of a given substitution; (3) \ruleref{Proj-Ext} explains why
substitution really looks like a (deeply-nested) pair.
